Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-07-31 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates: adding figures for the qualitative validation -- Section 4.2 ... text to come ...

A two-phase immiscible flow along homogeneous and parallel layers of contrasting permeability is initially simulated. During fluid displacement, crossflow between adjacent layers often occur due to viscous, capillary and/or gravitational forces in discontinuous spatial permeability distribution. Such preferential flows are shown in Figs.~\ref{DaweGrattoniExperiment_b}. In this case, crossflow behaviour from first to fourth quadrants of the domain is in good qualitative agreement with experiments conducted by \citet{dawe_2008}, Fig.~\ref{DaweGrattoniExperiment_a}.

>>>>

A two-phase immiscible flow along homogeneous and parallel layers of contrasting permeability is initially simulated. During fluid displacement, crossflow between adjacent layers often occur due to viscous, capillary and/or gravitational forces in discontinuous spatial permeability distribution. Such preferential flows are shown in Figs.~\ref{DaweGrattoniExperiment_b}. In this case, crossflow behaviour from first to fourth quadrants of the domain is in good qualitative agreement with experiments conducted by \citet{dawe_2008}, Fig.~\ref{DaweGrattoniExperiment_a}(b).
